### 2016-06-29 publications/Journal/abstract.tex
Updated abstract

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++14, but based on PythonPDEVS, which supports both conservative and optimistic synchronization.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol.
Performance results are compared to adevs, in terms of CPU time and memory usage.

>>>>

With the ever increasing complexity of simulation models, parallel simulation becomes necessary to perform simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11 and based on PythonPDEVS, supporting both conservative and optimistic synchronization protocols.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol.
A comparison is made to adevs in terms of CPU time and memory usage, to show that our modularity does not hinder performance.
We further allow for an external component to gather simulation statistics, on which runtime switching between the different synchronization protocols can be based.
Model allocation is also studied to see how our conservative and optimistic synchronization protocols are affected by good and bad allocations.
